Decompositions of congruence subgroups \\ of Chevalley groups

### 2016-09-01 paper.tex
Abstract small fix

\begin{abstract} 
We formulate and prove relative versions of several classical decompositions known in the theory of Chevalley groups over commutative rings.
We apply them to construct new factorizations in terms of $\SL_2$ and $\SL_n$ subgroups and to obtain upper estimates on the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
\end{abstract}

>>>>

\begin{abstract} 
We formulate and prove relative versions of several classical ``parabolic'' decompositions known in the theory of Chevalley groups over commutative rings.
We apply them to construct new factorizations in terms of $\SL_2$ and $\SL_n$ subgroups and to obtain upper estimates on the width of principal congruence subgroups in terms of Tits---Vaserstein generators.
Some of our results are new even in the absolute case and were previously studied only for groups over finite fields.
\end{abstract}
